Paper_analyses

### 2021-09-01 Paper_Analyses_subj_obje_arousal.Rmd
HR visualisations

>>>>

correlaation between the multiple signals

```{r}
table(is.na(db_full6new_hr_fix_stim_nt1.1$BIO_C))
db_full6new_hr_fix_stim_nt1.1$pup_basCor
db_full6new_hr_fix_stim_nt1.1$TTP.nSCR
db_full6new_hr_fix_stim_nt1.1$CDA.nSCR
db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif

# 
library(tidyverse)
library(ggplot2)
db_full6new_hr_fix_stim_nt1.1<- db_full6new_hr_fix_stim_nt1.1 %>%
  group_by(ssid)%>%
  mutate(BIO_CDA.PhasicMax_z = scale(BIO_CDA.PhasicMax, center = TRUE, scale = TRUE)[,1])%>%
  mutate(BIO_CDA.SCR_z = scale(BIO_CDA.SCR, center = TRUE, scale = TRUE)[,1])%>%
  mutate(BIO_CDA.ISCR_z = scale(BIO_CDA.ISCR, center = TRUE, scale = TRUE)[,1])%>%
  mutate(BIO_TTP.AmpSum_z = scale(BIO_TTP.AmpSum, center = TRUE, scale = TRUE)[,1])%>%
  mutate(BIO_CDA.AmpSum_z = scale(BIO_CDA.AmpSum, center = TRUE, scale = TRUE)[,1])%>%
  mutate(Bio_Mean_HR_dif_z = scale(Bio_Mean_HR_dif, center = TRUE, scale = TRUE)[,1])

          surface = TRUE,
          point.col = "blue")
          # point
db_full6new_hr_fix_stim_nt1.1%>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(BIO_CDA.PhasicMax_z, pup_basCor))+
  geom_point()+
  geom_smooth(method = lm, se = F)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt1.1%>%
  group_by(ssid)%>%
  mutate(cor_pup_scr = cor(BIO_CDA.PhasicMax_z, pup_basCor, use = "complete"))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(cor_pup_scr))+
  geom_histogram()

db_full6new_hr_fix_stim_nt1.1 %>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(BIO_CDA.SCR_z, Bio_Mean_HR_dif_z))+
  geom_point()+
  geom_smooth(method = lm, se = F)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt1.1 %>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(BIO_CDA.SCR_z, Bio_Mean_HR))+
  geom_point()+
  geom_smooth(method = lm, se = F)+
  ggpubr::stat_cor()

db_full6new_hr_fix_stim_nt1.1 %>%
  group_by(ssid)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(pup_basCor, Bio_Mean_HR))+
  geom_point()+
  # xlim()
  geom_smooth(method = lm, se = F)+
  ggpubr::stat_cor()
```
